---
title: "6306 Case Study 1"
author: "Hollie Gardner & Michael Weatherford"
date: "2/17/2020"
output:
  html_document: default
  pdf_document: default
  word_document: default
editor_options:
  chunk_output_type: inline
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries & packages}

#install packages
#install.packages("devtools")
#devtools::install_github("wmurphyrd/fiftystater")
#install.packages("ggrepel")

#libraries used
library(ggplot2)
library(imputeTS)
library(dplyr)
library(magrittr)

library(tidyr)
library(stringr)
library(tidyverse)
library(ggrepel)

library(RColorBrewer)
library(statebins)
library(naniar)
library(openintro)
library(fiftystater)
library(maps)
library(mapproj)
library(usmap)

```

# Question 1
**How many breweries are present in each state?**

With no supprises the states with higher populations have a higher number of breweries.  The general trend of more breweries for states 
with higher populations, is due to large populations being able to support a larger beer market.  There are more breweries in Democratic 
states/cities, this indicates that Democrats are more likely to purchase craft beer than Republicans.  This trend is consistant with 
typical younger Democratic voters primarily living on the East and West coast, and older Republican voters living in "fly over" states 
in the center of the United States.  These patterns give us an insight on the demographics of beer drinkers in each state.  The younger 
more Democratic states and cities are more adventerous in try new types of beers with no brand recognition, and the older more 
republican states are less experimental and are more habitial showing more brand loyality to established and well known breweries.

```{r bar chart with states}

# read in company data
Breweries <- read.csv("~/Desktop/Breweries.csv")

# pulling in state names from maps library
lookup = data.frame(state_code = state.abb, State = state.name) #makes a data frame with State name and state_codereviation. 
colnames(Breweries)[4]<- "state_code" # rename column to match lookup data
Breweries$state_code = str_trim(Breweries$state_code) # removing whitespace before each value to merge w/lookup
Breweries = merge(Breweries,lookup,"state_code") # make one dataset with state names and state_code *Lost brewery in DC
Breweries$State <- as.character(Breweries$State)
Breweries = rbind(Breweries, c("DC", 228, "DC Brau Brewing Company", "Washington", "District of Columbia"))

#bar chart for number of breweries by state in order without creating a new dataframe - HG
Breweries %>% 
  count(State) %>% #library(plyr) masks dplyr count()
  ggplot(aes(x=reorder(State, -n), y = n)) +
    geom_bar(stat="identity", fill="#C8102E", width=.8) + # budweiser red
    xlab("State") + ylab("Number of Breweries") + ggtitle("Number of Breweries by State") + 
    geom_text(aes(label=n), vjust=-0.3, size=2) +
    theme(axis.text.x = element_text(angle = 75, size = 7, hjust = 1))

```
```{r MW dataframe and barchart}

num_state = as.data.frame(table(Breweries$state_code))
colnames(num_state) <- c(as.character("state_code"),"Freq")
num_state$state_code <- as.character(num_state$state_code)
num_state2 <- data.frame("state_code" = as.character(c("AK", "AL", "AR", "AZ", "CA", "CO", "CT", "DC", "DE", "FL", "GA", "HI","IA", "ID", "IL", "IN", "KS", "KY", "LA", "MA", "MD", "ME", "MI", "MN","MO", "MS",  "MT", "NC", "ND", "NE", "NH", "NJ", "NM", "NV", "NY", "OH","OK", "OR", "PA", "PR", "RI", "SC", "SD", "TN", "TX", "UT", "VA", "VT","WA", "WI", "WV", "WY")),"fullState" = as.character(c("Alaska","Alabama" ,  "Arkansas", "Arizona","California" , "Colorado" , "Connecticut", "District of Columbia","Delaware" ,  "Florida" , "Georgia" ,"Hawaii","Iowa" ,"Idaho" , "Illinois" , "Indiana" ,  "Kansas" ,"Kentucky" , "Louisiana" , "Massachusetts", "Maryland" ,"Maine" ,"Michigan" , "Minnesota" , "Missouri" ,"Mississippi" ,  "Montana" ,"North Carolina","North Dakota", "Nebraska" , "New Hampshire" , "New Jersey" ,  "New Mexico" ,"Nevada" ,"New York" , "Ohio" , "Oklahoma" ,"Oregon" , "Pennsylvania" , "Puerto Rico", "Rhode Island" , "South Carolina", "South Dakota" ,"Tennessee" , "Texas" , "Utah" ,  "Virginia","Vermont" ,"Washington" , "Wisconsin", "West Virginia" , "Wyoming")))
num_state = merge(num_state, num_state2, by="state_code")
colnames(num_state)[3] <- "region"
colnames(num_state)[2] <- "Freq"
num_state$region <- as.character(num_state$region)

#Bar Chart for Number of Breweries in Each State - MW
theme_set(theme_classic())
ggplot(num_state, aes(x = reorder(state_code, -Freq), y=Freq)) + geom_bar(stat="identity", width = 0.5, fill="#C8102E") + 
  labs(title="Bar Chart", 
       subtitle="Number of Breweries per State", 
       caption="Note: Includes District of Columbia (DC)") +
  theme(axis.text.x = element_text(angle=65, vjust=0.6)) + 
  xlab("State") + ylab("Number of Breweries") +
  geom_text(aes(label=Freq), vjust=-0.3, size=3.5)
```

```{r statebin breweries}
#Plot Number of Breweries by State Bin
statebins_continuous(state_data = num_state, state_col = "region",
                     text_color = "white", value_col = "Freq",
                     brewer_pal="Greys", font_size = 3,
                     legend_title="Number of Breweries by State")
```

```{r us map of breweries}

#tidying for the fiftystater map
BreweriesCount = count(Breweries, State) #count up the occurrence in each state. 
colnames(BreweriesCount)[2] = "breweries" #change "n" to "breweries"
BreweriesCount$state <- tolower(BreweriesCount$State) # lower case state column for fiftystater

#bring in data from fifty_states package for coordinates
data("fifty_states") 

# map_id creates the aesthetic mapping to the state name column in BreweriesCount
p <- ggplot(BreweriesCount, aes(map_id = state)) + 
     geom_map(aes(fill = breweries), color="white", map = fifty_states) + 
     expand_limits(x = fifty_states$long, y = fifty_states$lat) +
     coord_map() +
  geom_text(data = fifty_states %>%
              group_by(id) %>%
              summarise(lat = mean(c(max(lat), min(lat))), long = mean(c(max(long), min(long)))) %>%
              mutate(state = id) %>% 
              left_join(BreweriesCount, by = "state"), aes(x = long, y = lat, label = breweries), size=2.75) +
  scale_x_continuous(breaks = NULL) + scale_y_continuous(breaks = NULL) +
  labs(x = "", y = "", title = "Number of Budweiser Breweries by State") +
  theme(legend.position = "right",
  panel.background = element_blank())


# add border boxes to AK/HI & change gradient colors to white, budweiser red, budweiser secondary red
brewerybystate <- p + fifty_states_inset_boxes()+ 
  scale_fill_gradient2(low="white", mid="#C8102E", high="#860419", midpoint = 15)
brewerybystate

```
## Process of cleaning the data from geonames
I created a new csv file to upload instead of making you run through the geoname one with 2million+ obs.
The process is shown and has been commented out.


```{r creating a map with number of breweries in cities}
#imported dataset: US.txt from geonames data US - http://download.geonames.org/export/dump/
#US <- read.delim("~/Downloads/US/US.txt", header=FALSE)

#using geonames data to create new dataframe with 4 columns
#us_cities <- cbind.data.frame(US$V2, US$V11, US$V5, US$V6)
#colnames(us_cities)[1] <- "City"
#colnames(us_cities)[2] <- "State"
#colnames(us_cities)[3] <- "lat"
#colnames(us_cities)[4] <- "lon"
#us_cities$cityandstate = paste(us_cities$City,us_cities$State) #creating a single column for city and state, because of duplicate city names
#us_cities$cityandstate <- as.character(us_cities$cityandstate) #make sure it's character before merge
#us_cities$cityandstate <- gsub("St", "Saint", us_cities$cityandstate) #fix abbreviations
#us_cities$cityandstate <- gsub("Mt", "Mount", us_cities$cityandstate)
#us_cities$cityandstate <- gsub(" ", "", us_cities$cityandstate) #remove whitespace
#us_cities$cityandstate<- gsub("\\.", "", us_cities$cityandstate) # remove period
#us_cities$cityandstate<- gsub("\\'", "", us_cities$cityandstate) # remove apostrophe
 
#brewcoord = Breweries #because i didn't want to screw up the original
#brewcoord$cityandstate= paste(brewcoord$City,brewcoord$state_code) #creating a new column
#num_city = as.data.frame(table(brewcoord$cityandstate)) #frequency of cities
#colnames(num_city)[1] <- "cityandstate"
#num_city$cityandstate <- as.character(num_city$cityandstate) #change to character to merge
#num_city$cityandstate <- gsub("St", "Saint", num_city$cityandstate) #fix abbreviations
#num_city$cityandstate <- gsub("Mt", "Mount", num_city$cityandstate)
#num_city$cityandstate<- gsub(" ", "", num_city$cityandstate)#remove whitespace
#num_city$cityandstate<- gsub("\\.", "", num_city$cityandstate) # remove period
#num_city$cityandstate<- gsub("\\'", "", num_city$cityandstate) # remove apostrophe

#finally... merging the two datasets
#Brews_City <- merge(num_city, us_cities,
#  by.x = "cityandstate",
#  all.x = TRUE,
#  all.y = FALSE)
#write.csv(Brews_City, "Brews_City.csv")

Brews_City <- read.csv("~/Desktop/Brews_City.csv")

#how many are missing lat?
sum(is.na(Brews_City$lat))

#visualization of missing data
vis_miss(Brews_City) + xlab("Data Columns")

```
```{r creating dataframe with lat/lon and freq}
#create new data set with lat and lon listed first
Brews_City2 = cbind.data.frame(Brews_City$lat, Brews_City$lon, Brews_City$Freq)
colnames(Brews_City2)[1] <- "lat"
colnames(Brews_City2)[2] <- "lon"
colnames(Brews_City2)[3] <- "freq"

#omit the 10 breweries that have NA values
Cities=na.omit(Brews_City2) 

#create map with number of breweries by city
us <- map_data('usa') #data from library(maps)
Cities$freqfact <- cut(Cities$freq, breaks=c(0, 1, 4, Inf), labels=c("1 brewery", "2-4 breweries", "5 or more breweries")) #create new column for factor levels
Cities$freqfact <-as.factor(Cities$freqfact)  #changing to factor
ggplot()+
  geom_polygon(data=us, aes(x=long, y=lat, group = group), colour="grey20", fill="white") +
  geom_point(data = Cities, aes(x=lon, y = lat, color=freqfact, size=freqfact)) +     scale_color_manual(values=c("#808080","#C8102E","blue")) + scale_size_manual(values=c(1.5,4,6), guide=FALSE) + labs(color='Number of Breweries')  + 
  coord_map(xlim=c(-130, -65), ylim=c(25,50)) + xlab("") + ylab("") + ggtitle("Cities with Breweries") +
  theme_bw() 
```

# Question 2
**Merge beer data with the breweries data. Print the first 6 observations and the last six observations to check the merged file.  (RMD only, this does not need to be included in the presentation or the deck.)**

```{r merging Beers and Breweries}

Beers <- read.csv("~/Desktop/Beers.csv") # read in beer data
colnames(Beers)[5] = "Brew_ID" #change "Brewery_ID" to "Brew_ID"

Beers_Breweries = merge(Breweries, Beers,"Brew_ID", all=TRUE) # merge while keeping all values
colnames(Beers_Breweries)[3] = "Brewery_Name"  # change "Name.x" to "Brewery"
colnames(Beers_Breweries)[5] = "State_Name" 
colnames(Beers_Breweries)[6] = "Beer_Name" 
head(Beers_Breweries, n=6) # first six observations
tail(Beers_Breweries,n=6) # last six obervations

```

# Question 3
**Address the missing values in each column.**

Looking at the data you have provided our firm, we conducted a quality check to ensure we are giving you the best and most accurate 
answers possible.  There were only two variables missing data, ABV and IBU.  Although not required federally, it appears to be common 
practice to label and publish individual beers ABV, we assumed the missing 2.75% of ABV data were missing completely at random.  The IBU 
was missing a substantial 41.7% of the data.  Most of the data represents small micro breweries that change their SKUs a lot, and are 
not willing to incur an additional expense on test each batch of craft beer for an IBU rating.  We assumed the IBU data was missing not 
at random.  Since over 40% of the dataset was missing IBU we did not want to throw out all the addition data so we replace empty values 
with the data set mean IBU.

```{r missing values}
#visualization of the observations with missing values by column
vis_miss(Beers_Breweries) + xlab("Data Columns from Merged Set")

#replacing all NA values with the mean
Beers_Breweries <- na_mean(Beers_Breweries, option = "mean") 

#addressing other suspect values
#remove can'd aid - looks to be a foundation and not a beer
Beers_Breweries <- Beers_Breweries[Beers_Breweries$Beer_ID != 1790, ]

# The CROWLER is a portmanteau of can + growler. It's a can that's the size of and is essentially a growler.
Beers_Breweries <- Beers_Breweries[Beers_Breweries$Beer_ID != 1796, ]

# Cedar Creek Special Release is just a marketing title and not a beer
Beers_Breweries <- Beers_Breweries[Beers_Breweries$Beer_ID != 2210, ]

# changing remaining missing values to the column mean
Beers_Breweries <- na_mean(Beers_Breweries, option = "mean") 

```

## Question 4, ABV

**Compute the median alcohol content and international bitterness unit for each state. Plot a bar chart to compare.**

Looking at the barchart for median ABV by state, you can see the range is fairly consistant from slightly over 6% on the high end and 
about 5% on the low end with Utah being an outlier.  Showing the median beer drinker is enjoying beer at a modest level of alcohol 
content.  The bar chart of median IBU by state Shows WV enjoying a high level of bitterness compared to KS low tolerance for bitterness.
There is a much larger range on this metric than the ABV indicating that geographic areas are more or less tolerant to the bitterness 
flavor profile, keep in mind the states with fairly consistant IBU medians in the center of the bar chart are heavily affected by the 
40% of missing data and is due to us filling in the missing data with the mean.

```{r Median ABV barchart}

#Median ABV & IBU by State
# create dataframe for median ABV by state, **note to MW - I changed this to avoid using the plyr package**
med_ABV <- Beers_Breweries %>%
  group_by(state_code) %>%
  summarize(medianABV = median(ABV))

#create dataset for median IBU by state
med_IBU<- Beers_Breweries %>%
  group_by(state_code) %>%
  summarize(medianIBU = median(IBU))

# merging median ABV and median IBU
med_bar = merge(med_ABV, med_IBU, by="state_code")
colnames(med_bar)[2] <- "Median_ABV"
colnames(med_bar)[3] <- "Median_IBU"

#Median ABV Map Viz
theme_set(theme_classic())
ggplot(med_bar, aes(x = reorder(state_code, -Median_ABV), y=Median_ABV)) + geom_bar(stat="identity", width = 0.5, fill="#C8102E") + 
  labs(subtitle="Median ABV by State", 
       caption="Note: Includes District of Columbia (DC)") +
  theme(axis.text.x = element_text(angle=90, vjust=0.6)) + 
  xlab("State") + ylab("Alcohol by Volume (ABV)") 

```
# Question 4, IBU

**Compute the median alcohol content and international bitterness unit for each state. Plot a bar chart to compare.**

```{r Median IBU chart}
#Median IBU Map Viz
theme_set(theme_classic())
ggplot(med_bar, aes(x = reorder(state_code, -Median_IBU), y=Median_IBU)) + geom_bar(stat="identity", width = 0.6, fill="#C8102E") + 
  labs(subtitle="Median IBU by State", 
       caption="Note: Includes District of Columbia (DC)") +
  theme(axis.text.x = element_text(angle=90, vjust=0.6)) + 
  xlab("State") + ylab("International Bitterness Unit (IBU)") 

```
# Question 5

**Which state has the maximum alcoholic (ABV) beer? Which state has the most bitter (IBU) beer?**

The beers with the highest ABV were primarily in the center of the United States (CO, KY, IN).  This could indicate the center of the US 
puts more importance on alcohol content than taste.  The states with the maximum IBU follows fairly close the map for number of 
breweries per capita.  Once again confirming that younger democratic beer drinkers are more adventerous and willing to exlore beers with 
higher bitterness flavor profile.

```{r}
library(plyr)
#Maximums question
max_ABV = data.frame(ddply(Beers_Breweries,~state_code,summarise,max=max(ABV)))
max_IBU = data.frame(ddply(Beers_Breweries,~state_code,summarise,max=max(IBU)))
colnames(max_ABV)[1] <- "state_code"
colnames(max_IBU)[1] <- "state_code"
max_ABV = merge(max_ABV, num_state2, by="state_code")
max_IBU = merge(max_IBU, num_state2, by="state_code")
max_ABV$fullState <- as.character(max_ABV$fullState)
max_IBU$fullState <- as.character(max_IBU$fullState)

#Max Viz ABV
statebins_continuous(state_data = max_ABV, state_col = "fullState",
                     text_color = "white", value_col = "max",
                     brewer_pal="Greys", font_size = 3,
                     legend_title="Max ABV by State")

#Max Viz IBU
statebins_continuous(state_data = max_IBU, state_col = "fullState",
                     text_color = "white", value_col = "max",
                     brewer_pal="Greys", font_size = 3,
                     legend_title="Max IBU by State")

#Obs with Max ABV & Value
max(Beers_Breweries$ABV)
which.max(Beers_Breweries$ABV)

#Upslope Brewing Company -	Lee Hill Series Vol. 5 - Belgian Style Quadrupel Ale	12.8

max(Beers_Breweries$IBU)
which.max(Beers_Breweries$IBU)

#Astoria Brewing Company - Bitter Bitch Imperial IPA	138

```
# Question 6

**Comment on the summary statistics and distribution of the ABV variable.**
When checking our assumptions, the ABV is normally distributed as evidenced by the QQPlot. The histogram further reinforces this with a mostly normal distribution, with some slight right skewness with some beers that test the limits of the ABV content. 

```{r Question 6}
#Statistics Summary for ABV
Beers_Breweries %>% ggplot(aes(x = ABV)) + geom_histogram(color="black", fill="#C8102E") + ggtitle("Histogram of ABV") + geom_vline(aes(xintercept=mean(ABV)), color="blue", linetype="dashed", size=1) + geom_density(alpha=.2, fill="black") 

qqnorm(Beers_Breweries$ABV, pch = 1, frame = FALSE)
qqline(Beers_Breweries$ABV, col = "#C8102E", lwd = 2)
```

# Question 7

**Is there an apparent relationship between the bitterness of the beer and its alcoholic content? Draw a scatter plot.  Make your
best judgment of a relationship and EXPLAIN your answer.**

Looking at ABV and IBU there is a positive linear correlation.  As the beer has higher alcohol content it tends to have a higher IBU.  
More importantly, this graph shows the flavor profile that most breweries are producing their beers at.  Around 5% ABV and 25 IBU we see 
a dense "sweet spot" of beers.  If a brewery wanted to reach the largest number of consumers this is the ABV and IBU most beer drinkers 
enjoy.  As you move away from this sweet spot the number of beers is substantially lower and less dense.  We reccommend that your core 
SKUs that are trying to reach the most consumers and bring in the most revenue are close to this area, with much smaller percent of 
experimental beers outside the sweet spot.  It is good to note at about 45 IBU there is a spot of high density and that is due to the 
mean being filled in for the missing IBU measurements and is not a accurate representation of the most sought after beer flavor profile.

```{r scatter plot bitterness & alc content}
#Scatter Plot Viz
ggplot(Beers_Breweries, aes(x=ABV, y=IBU)) + geom_point(color="#C8102E") + geom_smooth(method=lm) + geom_density_2d(color="black")

```

# Question 8

**Budweiser would also like to investigate the difference with respect to IBU and ABV between IPAs (India Pale Ales) and other types of Ale (any beer with “Ale” in its name other than IPA).  You decide to use KNN classification to investigate this relationship.  Provide statistical evidence one way or the other. You can of course assume your audience is comfortable with percentages … KNN is very easy to understand conceptually.**

With 84% accuracy(k=5), we are able to predict if an ale is an IPA or not using the given ales in the Beers dataset. 

```{r knn IBU and ABV}

#knn question - load libraries
library(class)
library(caret)
library(e1071)

IPAorAle = dplyr::filter(Beers_Breweries, grepl('IPA|Ale', Style))
IPAorAle$Type <- ifelse(grepl("IPA", IPAorAle$Style), "IPA", "Ale")
summary(IPAorAle)

set.seed(6)
splitPerc = .75
trainIndices = sample(1:dim(IPAorAle)[1],round(splitPerc * dim(IPAorAle)[1]))
train = IPAorAle[trainIndices,]
test = IPAorAle[-trainIndices,]

IPAorAle %>% ggplot(aes(x = ABV, IBU, color = Type)) + geom_point() + scale_color_manual(values = c("#C8102E", "#000000")) + ggtitle("IPA and Ale Beer Styles")

# k = 5
classifications = knn(train[,c(8,9)],test[,c(8,9)],train$Type, prob = TRUE, k = 5)
table(test$Type,classifications)
confusionMatrix(table(test$Type,classifications))

```

# Question 9

**Knock their socks off!  Find one other useful inference from the data that you feel Budweiser may be able to find value in.  You must convince them why it is important and back up your conviction with appropriate statistical evidence.** 

The boxplots of the selected style groups demonstrate that there is a difference in median ABVs by the style with IPAs, Stouts, and Porters having higher ABV medians. 

```{r Question 9 analysis}

#histogram of American IPA ABV distribution
AmericanIPA <- Beers_Breweries[Beers_Breweries$Style == "American IPA",]
Beers_Breweries[Beers_Breweries$Style == "American IPA",] %>%   
  ggplot(mapping = aes(x = ABV)) +
  geom_histogram(bins=15, color="black", fill="#C8102E",) + ggtitle("American IPA IBU distribution")

#scatter plot American IPA ABV vs. IBU
ggplot(AmericanIPA, aes(x=ABV, y=IBU)) + geom_point(color="#C8102E") + geom_smooth(method=lm)

#bar chart of number of beers per style
freqStyle = as.data.frame(table(Beers_Breweries$Style))
freqStyle %>%
  ggplot(aes(x=reorder(Var1, -Freq), y = Freq)) +
    geom_bar(stat="identity", fill="#C8102E", width=.8) + # budweiser red
    xlab("Style") + ylab("Number of Beers") + ggtitle("Number of Beers by Style") + 
    geom_text(aes(label=Freq), vjust=-0.3, size=2) +
    theme(axis.text.x = element_text(angle = 75, size = 7, hjust = 1))

#creating a new Type column to hold broader Style groups
Stout = dplyr::filter(Beers_Breweries, grepl('Stout', Style))
Stout$Type <- "Stout"

Porter = dplyr::filter(Beers_Breweries, grepl('Porter', Style))
Porter$Type <- "Porter"

Lager = dplyr::filter(Beers_Breweries, grepl('Lager', Style))
Lager$Type <- "Lager"

Witbier = dplyr::filter(Beers_Breweries, grepl('Witbier', Style))
Witbier$Type <- "Witbier"

Pilsner = dplyr::filter(Beers_Breweries, grepl('Pilsner|Pilsener', Style))
Pilsner$Type <- "Pilsner"

#merging dataframes back together
Beers_Types = rbind(Stout, Porter, IPAorAle, Lager, Pilsner, Witbier)

#plot ABV boxplot by selected style groups  
p <- ggplot(Beers_Types, aes(x=Type, y=ABV, fill=Type)) + 
  geom_boxplot() + xlab("Style Group") + ylab("ABV Distribution") + ggtitle("Boxplots of ABV by Selected Style Groups")
  
p + scale_fill_manual(values=c("#860419","#C8102E","#ED3F48", "#FF6263", "#FF8380","#FFA59E","#FFF4F1"))

#plot IBU boxplot by selected style groups    
p <- ggplot(Beers_Types, aes(x=Type, y=IBU, fill=Type)) + xlab("Style Group") + ylab("IBU Distribution") + geom_boxplot() + ggtitle("Boxplots of IBU by Selected Style Groups")

p + scale_fill_manual(values=c("#860419","#C8102E","#ED3F48", "#FF6263", "#FF8380","#FFA59E","#FFF4F1"))

#facet wrap by ABV
ggplot(data = Beers_Types) + 
geom_histogram(mapping = aes(x = ABV), fill="#C8102E", bins=10) + ggtitle("ABV Histogram of Select Style Groups") + xlab("ABV by Style Group") + ylab("Number of Beers") +
facet_grid(~Type)

#facet wrap by IBU
ggplot(data = Beers_Types,) + 
geom_histogram(mapping = aes(x = IBU), fill="#C8102E", bins=10) + ggtitle("IBU Histogram of Select Style Groups")+
facet_grid(~Type)

```
