---
title: "Case Study 2"
author: "Hollie Gardner"
date: "4/06/2020"
editor_options: 
  chunk_output_type: console
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#Overview
DDSAnalytics is an analytics company that specializes in talent management solutions for Fortune 100 companies. Talent management is defined as the iterative process of developing and retaining employees. Talent management includes:
•	workforce planning, 
•	employee training programs, 
•	identifying high-potential employees
•	reducing/preventing voluntary employee turnover (attrition).
To gain a competitive edge over its competition, DDSAnalytics is planning to leverage data science for talent management. The executive leadership has identified predicting employee turnover as its first application of data science for talent management. Before the business greenlights the project, they have tasked your data science team to conduct an analysis of existing employee data. Audience is the CEO and CFO of Frito Lay (your client). The CEO is a statistician and the CFO has had only one class in statistics.  

#Analysis

You have been given a dataset (CaseStudy2-data.csv) to do a data analysis to identify factors that lead to attrition.  
•	Identify the top three factors that contribute to turnover (backed up by evidence provided by analysis). 
•	There may or may not be a need to create derived attributes/variables/features. 
•	Identify any job role specific trends that may exist in the data set (e.g., “Data Scientists have the highest job satisfaction”)
•	Provide any other interesting trends and observations from your analysis. 
•	The analysis should be backed up by robust experimentation and appropriate visualization. Experiments and analysis must be conducted in R. 
•	Build a model to predict attrition.  



```{r Libraries}

colors2 <- c("#AB0E14", "#F1B11B")
colors3 <- c("#EF1C24", "#F1B11B","#000000")
colors4 <- c("#AB0E14", "#F1B11B", "#EF1C24","#000000")
colors5 <- c("#AB0E14", "#F1B11B", "#EF1C24", "#F1B11B", "#957531")
colors6 <- c("#AB0E14", "#F1B11B", "#EF1C24", "#F1B11B", "#957531", "#000000")
  
library(GGally)
library(ggplot2)
library(corrplot) 
library(naniar) #missing value vis
library(MASS)  #chi-sq table
library(magrittr)
library(dplyr)
library(caret)
library(e1071)
library(class)


CaseStudy2 <- read.csv("~/Desktop/CaseStudy2-data.csv")

```
#Tidying Data
There were a number of variables that were defined as numeric, but were actually representations of factors. I removed the Employee Count, Over 18, and Standard Hours variables because these were all the same. I also didn't the Employee ID number for this analysis.

```{r}

CaseStudy2$JobSatisfaction <- as.factor(CaseStudy2$JobSatisfaction)
CaseStudy2$EnvironmentSatisfaction <- as.factor(CaseStudy2$EnvironmentSatisfaction)
CaseStudy2$JobLevel <- as.factor(CaseStudy2$JobLevel)
CaseStudy2$JobInvolvement <- as.factor(CaseStudy2$JobInvolvement)
CaseStudy2$PerformanceRating <- as.factor(CaseStudy2$PerformanceRating)
CaseStudy2$RelationshipSatisfaction <- as.factor(CaseStudy2$RelationshipSatisfaction)
CaseStudy2$StockOptionLevel <- as.factor(CaseStudy2$StockOptionLevel)
CaseStudy2$WorkLifeBalance <- as.factor(CaseStudy2$WorkLifeBalance)
CaseStudy2$Education <- as.factor(CaseStudy2$Education)

#removing unnecessary columns
#Employee Count is all 1
CaseStudy2$EmployeeCount <- NULL

#Employee Number is an unnecessary ID number
CaseStudy2$EmployeeNumber <- NULL

#All employees are Over18
CaseStudy2$Over18 <- NULL

#All Employee Standard Hours are 80
CaseStudy2$StandardHours <-NULL
```
#Checking for missing values
There are none.
```{r}
#missing values - all are present and no NA
#vis_miss(CaseStudy2)
#sum(is.na(CaseStudy2))
```
#Percentage of Attrition in Employees
16.1% of the 870 employees have left Frito Lay.

```{r}

CaseStudy2 %>% 
  count(Attrition) %>% 
  mutate(pct = prop.table(n)) %>%     
  ggplot(aes(x = Attrition, y = pct, fill = Attrition, label = scales::percent(pct))) + 
    geom_col(position = 'dodge') + 
    geom_text(position = position_dodge(width = .9),    # move to center of bars
        vjust = -0.5,    # nudge above top of bar
        size = 3) + ylab("Percentage of Employees") + ggtitle("Frito Lay Attrition") + scale_y_continuous(labels = scales::percent) + scale_fill_manual(values = colors2)

```
#Attrition by Gender
Female - 14.97%
Male - 16.86%

The difference in percentage of attrition is not significant: 
X-squared = 0.42363, df = 1, p-value = 0.5151


```{r}
#bar chart with gender and attrition
CaseStudy2 %>%
  ggplot(aes(x= Gender, fill = Attrition)) +
  geom_bar(stat = "count") + scale_fill_manual(values = colors2) + 
  ggtitle("Percentage of Attrition by Gender") + ylab("Employee Count")


(sum(CaseStudy2$Gender == "Female" & CaseStudy2$Attrition == "Yes")/sum(CaseStudy2$Gender == "Female"))* 100

(sum(CaseStudy2$Gender == "Male" & CaseStudy2$Attrition == "Yes")/sum(CaseStudy2$Gender == "Male"))* 100

Gtbl = table(CaseStudy2$Gender, CaseStudy2$Attrition) 
Gtbl

chisq.test(Gtbl)

```
#Performance Rating
We are only interested in retention of employees with a 3 or 4 performance rating, since performance ratings of under 3 are likely on a performance plan or have been terminated. 
Employees with a 3 performance rating had 15.85% attrition. Employees with a 4 performance rating had a slightly higher percentage with 17.24% leaving. While factors like star performers being recruited to other companies could play a part in the increase, the slight difference in percentage is not significant according to Pearson's chi-sq test (p=.74).

```{r}
CaseStudy2 %>%
  ggplot(aes(x= PerformanceRating, fill = Attrition)) +
  geom_bar(stat = "count") + scale_fill_manual(values = colors2) + 
  ggtitle("Percentage of Attrition by Performance Rating") + ylab("Employee Count")

(sum(CaseStudy2$PerformanceRating == "3" & CaseStudy2$Attrition == "Yes")/sum(CaseStudy2$PerformanceRating == "3"))* 100

(sum(CaseStudy2$PerformanceRating == "4" & CaseStudy2$Attrition == "Yes")/sum(CaseStudy2$PerformanceRating == "4"))* 100

PRtbl = table(CaseStudy2$PerformanceRating, CaseStudy2$Attrition) 
PRtbl

chisq.test(PRtbl)

```
```
#Department & JobRole

There is a relationship between department and attrition (X-squared = 9.329, df = 2, p-value = 0.009424). There is an even more significant relationship between job role and attrition(X-squared = 60.543, p-value = 3.647e-10), with the lowest percentage being 1.96% of Research Directors leaving versus 45.86% of sales representatives leaving. The national trend for sales representative attrition is 27%, which makes this number higher than expected.

Healthcare Representative - 10.5%
Human Resources - 22.2%
Laboratory Technician - 19.6%
Manager - 7.84%
Manufacturing Director - 2.29%
Research Director - 1.96%
Research Scientist - 18.6%
Sales Executive - 16.5%
Sales Representative - 45.28%
```{r}

CaseStudy2 %>%
  ggplot(aes(x= JobRole, fill=Attrition)) +
  geom_bar(stat = "count") + scale_fill_manual(values = colors5) + 
  ggtitle("Percentage of Attrition by Job Role") + ylab("Employee Count")

(sum(CaseStudy2$JobRole == "Healthcare Representative" & CaseStudy2$Attrition == "Yes")/sum(CaseStudy2$JobRole == "Healthcare Representative"))* 100

(sum(CaseStudy2$JobRole == "Human Resources" & CaseStudy2$Attrition == "Yes")/sum(CaseStudy2$JobRole == "Human Resources"))* 100

(sum(CaseStudy2$JobRole == "Manager" & CaseStudy2$Attrition == "Yes")/sum(CaseStudy2$JobRole == "Manager"))* 100

(sum(CaseStudy2$JobRole == "Manufacturing Director" & CaseStudy2$Attrition == "Yes")/sum(CaseStudy2$JobRole == "Manufacturing Director"))* 100

(sum(CaseStudy2$JobRole == "Research Director" & CaseStudy2$Attrition == "Yes")/sum(CaseStudy2$JobRole == "Research Director"))* 100

(sum(CaseStudy2$JobRole == "Research Scientist" & CaseStudy2$Attrition == "Yes")/sum(CaseStudy2$JobRole == "Research Scientist"))* 100

(sum(CaseStudy2$JobRole == "Laboratory Technician" & CaseStudy2$Attrition == "Yes")/sum(CaseStudy2$JobRole == "Laboratory Technician"))* 100

(sum(CaseStudy2$JobRole == "Sales Executive" & CaseStudy2$Attrition == "Yes")/sum(CaseStudy2$JobRole == "Sales Executive"))* 100

(sum(CaseStudy2$JobRole == "Sales Representative" & CaseStudy2$Attrition == "Yes")/sum(CaseStudy2$JobRole == "Sales Representative"))* 100

(sum(CaseStudy2$PerformanceRating == "4" & CaseStudy2$Attrition == "Yes")/sum(CaseStudy2$PerformanceRating == "4"))* 100

```
#Chi-Square Test - Contingency Table for Department & Job Role

                          No Yes
  Human Resources         29   6
  Research & Development 487  75
  Sales                  214  59
  
  	Pearson's Chi-squared test

data:  (tbl)
X-squared = 9.329, df = 2, p-value = 0.009424
                           
                             No Yes
  Healthcare Representative  68   8
  Human Resources            21   6
  Laboratory Technician     123  30
  Manager                    47   4
  Manufacturing Director     85   2
  Research Director          50   1
  Research Scientist        140  32
  Sales Executive           167  33
  Sales Representative       29  24

	Pearson's Chi-squared test

data:  JobRoletbl
X-squared = 60.543, df = 8, p-value = 3.647e-10

```{r}
tbl = table(CaseStudy2$Department, CaseStudy2$Attrition) 
tbl    

chisq.test((tbl))

JobRoletbl = table(CaseStudy2$JobRole, CaseStudy2$Attrition) 
JobRoletbl                
chisq.test(JobRoletbl)

```
#Age
I converted the numeric age to factor. There is evidence(Pearson's chi-squared X-squared = 27.929, df = 4, p-value = 1.289e-05) that younger or early career employees are not sticking around with 30% of employees age 18-24 and 22% of employees age 25-33 leaving as compared to 10% of employees age 34-44 and 12% of employees age 45-55 leaving. 

```{r}
CaseStudy2$Age_factor = cut(CaseStudy2$Age, breaks = c(18,25,33,45,55,100), labels = c("18-24","25-33","34-44","45-54","55 and Older"))

CaseStudy2 %>%
  ggplot(aes(x= Age_factor, fill=Attrition)) +
  geom_bar(stat = "count") + scale_fill_manual(values = colors5) + 
  ggtitle("Percentage of Attrition by Age") + ylab("Employee Count")

(sum(CaseStudy2$Age_factor == "1" & CaseStudy2$Attrition == "Yes")/sum(CaseStudy2$Age_factor == "1"))*100
max(CaseStudy2$Age)

AFtbl = table(CaseStudy2$Age_factor, CaseStudy2$Attrition) 
AFtbl                
chisq.test(AFtbl)
```
#Education
Not significant
```{r}
CaseStudy2 %>%
  ggplot(aes(x= Education, fill=Attrition)) +
  geom_bar(stat = "count") + scale_fill_manual(values = colors5) + 
  ggtitle("Percentage of Attrition by Education") + ylab("Employee Count")

Educationtbl = table(CaseStudy2$Education, CaseStudy2$Attrition) 
Educationtbl

chisq.test(Educationtbl)

```
#Business Travel
Significant p=.0499
```{r}

CaseStudy2 %>%
  ggplot(aes(x= BusinessTravel, fill=Attrition)) +
  geom_bar(stat = "count") + scale_fill_manual(values = colors5) + 
  ggtitle("Percentage of Attrition by Amount of Business Travel") + ylab("Employee Count")

Traveltbl = table(CaseStudy2$BusinessTravel, CaseStudy2$Attrition) 
Educationtbl

chisq.test(Traveltbl)

```
#Env Satisfaction Travel - 
Significant p=0.01
```{r}

CaseStudy2 %>%
  ggplot(aes(x= EnvironmentSatisfaction, fill=Attrition)) +
  geom_bar(stat = "count") + scale_fill_manual(values = colors5) + 
  ggtitle("Percentage of Attrition by Environment Satisfaction") + ylab("Employee Count")

Envtbl = table(CaseStudy2$EnvironmentSatisfaction, CaseStudy2$Attrition) 
Envtbl

chisq.test(Envtbl)
```
#JobInvolvement - 
Significant p-value = 5.211e-09
```{r}

CaseStudy2 %>%
  ggplot(aes(x= JobInvolvement, fill=Attrition)) +
  geom_bar(stat = "count") + scale_fill_manual(values = colors5) + 
  ggtitle("Percentage of Attrition by Environment Satisfaction") + ylab("Employee Count")

JItbl = table(CaseStudy2$JobInvolvement, CaseStudy2$Attrition) 
JItbl

chisq.test(JItbl)

```
#Stock Level Options
Significant p-value = 3.724e-12
```{r}
CaseStudy2 %>%
  ggplot(aes(x= StockOptionLevel, fill=Attrition)) +
  geom_bar(stat = "count") + scale_fill_manual(values = colors5) + 
  ggtitle("Percentage of Attrition by Stock Option") + ylab("Employee Count")

SOtbl = table(CaseStudy2$StockOptionLevel, CaseStudy2$Attrition) 
chisq.test(SOtbl)


```
#Overtime
p-value = 2.333e-15
```{r}
CaseStudy2 %>%
  ggplot(aes(x= OverTime, fill=Attrition)) +
  geom_bar(stat = "count") + scale_fill_manual(values = colors5) + 
  ggtitle("Percentage of Attrition by OverTime") + ylab("Employee Count")

ottbl = table(CaseStudy2$OverTime, CaseStudy2$Attrition) 
chisq.test(ottbl)
```

#Work Life Balance - significant p-value=0.0025
```{r}
CaseStudy2 %>%
  ggplot(aes(x= WorkLifeBalance, fill=Attrition)) +
  geom_bar(stat = "count") + scale_fill_manual(values = colors5) + 
  ggtitle("Percentage of Attrition by Work Life Balance") + ylab("Employee Count")

wlbtbl = table(CaseStudy2$WorkLifeBalance, CaseStudy2$Attrition) 
wlbtbl
chisq.test(wlbtbl)
```

#Relationship Satisfaction - significant p-value=0.0025
```{r}
CaseStudy2 %>%
  ggplot(aes(x= RelationshipSatisfaction, fill=Attrition)) +
  geom_bar(stat = "count") + scale_fill_manual(values = colors5) + 
  ggtitle("Manager Relationship Satisfaction") + ylab("Employee Count")

rstbl = table(CaseStudy2$RelationshipSatisfaction, CaseStudy2$Attrition) 
rstbl
chisq.test(rstbl)
```

##Boxplots of Numeric Data
#Attrition=No group has higher median
Age 2
DailyRate 5
MonthlyIncome 18
MonthlyRate 19
NumCompaniesWorked 20
TotalWorkingYears 26
Training 27
Years at Company 29
Years in current role 30
Years since last promotion 31

#Attrition=Yes has higher median
DistanceFromHome 7
Hourlyrate 12

``` {r attrition relationship EDA}
#boxplot of attrition by age[2] - Different (Yes is lower)
CaseStudy2 %>% ggplot(aes(x = Attrition, y = Age, fill = Attrition)) + geom_boxplot(color = "black") + scale_fill_manual(values = colors2)

#boxplot of attrition by daily rate[5] - Different (No is higher)
CaseStudy2 %>% ggplot(aes(x = Attrition, y = DailyRate, fill=Attrition)) + geom_boxplot(color = "black") + scale_fill_manual(values = colors2) 

#boxplot of attrition by distance from home[7] - Different (Yes is higher)
CaseStudy2 %>% ggplot(aes(x = Attrition, y = DistanceFromHome, fill=Attrition)) + geom_boxplot(color="black") + scale_fill_manual(values = colors2) + ggtitle("Boxplot of Distribution of Distance from Home Grouped by Attrition")

#boxplot attrition by hourly rate[] - Different (Yes is higher (PT? Sales & Commission?))
CaseStudy2 %>% ggplot(aes(x = Attrition, y = HourlyRate, fill=Attrition)) + geom_boxplot(color="black") + scale_fill_manual(values = colors2)  + ggtitle("Distribution of Hourly Rate by Attrition")

#boxplot attrition by monthly income - Different (No is higher)
CaseStudy2 %>% ggplot(aes(x = Attrition, y = MonthlyIncome, fill=Attrition)) + geom_boxplot(color="black") + scale_fill_manual(values = colors2) + ggtitle("Distribution of Monthly Income by Attrition")

#boxplot attrition by monthly rate - Different (No is higher)
CaseStudy2 %>% ggplot(aes(x = Attrition, y = MonthlyRate, fill=Attrition)) + geom_boxplot(color="black") + scale_fill_manual(values = colors2) + ggtitle("Distribution of Monthly Rate by Attrition")

#boxplot attrition by number of companies worked - Different (yes is lower)
CaseStudy2 %>% ggplot(aes(x = Attrition, y = NumCompaniesWorked, fill=Attrition)) + geom_boxplot(color="black") + scale_fill_manual(values = colors2) 

#boxplot attrition by percent salary raise - Same
CaseStudy2 %>% ggplot(aes(x = Attrition, y = PercentSalaryHike, fill=Attrition)) + geom_boxplot(color="black") + scale_fill_manual(values = colors2) 

#boxplot attrition by total working years - Different (Yes is lower)
CaseStudy2 %>% ggplot(aes(x = Attrition, y = TotalWorkingYears, fill=Attrition)) + geom_boxplot(color="black") + scale_fill_manual(values = colors2) 

#boxplot attrition by training last year - Different (Yes is lower)
CaseStudy2 %>% ggplot(aes(x = Attrition, y = TrainingTimesLastYear, fill=Attrition)) + geom_boxplot(color="black") + scale_fill_manual(values = colors2) + ggtitle("Distribution of Number of Training Times Grouped by Attrition")

#boxplot attrition by years at company - Different (Yes is lower)
CaseStudy2 %>% ggplot(aes(x = Attrition, y = YearsAtCompany, fill=Attrition)) + geom_boxplot(color="black") + scale_fill_manual(values = colors2) 

#boxplot attrition by years in current role - Close (Yes is lower)
CaseStudy2 %>% ggplot(aes(x = Attrition, y = YearsInCurrentRole, fill=Attrition)) + geom_boxplot(color="black") + scale_fill_manual(values = colors2) 

#boxplot attrition by years since last promotion - Same
CaseStudy2 %>% ggplot(aes(x = Attrition, y = YearsSinceLastPromotion, fill=Attrition)) + geom_boxplot(color="black") + scale_fill_manual(values = colors2) 

#boxplot attrition by years with current manager - Different (Yes is lower)
CaseStudy2 %>% ggplot(aes(x = Attrition, y = YearsWithCurrManager, fill=Attrition)) + geom_boxplot(color="black") + scale_fill_manual(values = colors2) + ggtitle("Boxplot of Years with Current Manager Grouped by Attrition")

#boxplot training session - Different (Yes is lower)
CaseStudy2 %>% ggplot(aes(x = Attrition, y = YearsWithCurrManager, fill=Attrition)) + geom_boxplot(color="black") + scale_fill_manual(values = colors2) + ggtitle("Boxplot of Years with Current Manager Grouped by Attrition")

```
#Predicting Attrition with Naive Bayes

```{r naiveBayes}

#NBmodel1 <- naiveBayes(Attrition ~ ., data = CaseStudy2, laplace = 3)
#CM1 = confusionMatrix(table(NBmodel1, CaseStudy2$Attrition))
#CM1

```

```{r}

CaseStudy2CompSetNoAttrition <- read.csv("~/Desktop/MSDS_6306_Doing-Data-Science-Master/Unit 14 and 15 Case Study 2/CaseStudy2CompSet No Attrition.csv")

#Match NoSalary dataframe clean up to CaseStudy2
CaseStudy2CompSetNoAttrition$JobSatisfaction <- as.factor(CaseStudy2CompSetNoAttrition$JobSatisfaction)
CaseStudy2CompSetNoAttrition$EnvironmentSatisfaction <- as.factor(CaseStudy2CompSetNoAttrition$EnvironmentSatisfaction)
CaseStudy2CompSetNoAttrition$JobLevel <- as.factor(CaseStudy2CompSetNoAttrition$JobLevel)
CaseStudy2CompSetNoAttrition$JobInvolvement <- as.factor(CaseStudy2CompSetNoAttrition$JobInvolvement)
CaseStudy2CompSetNoAttrition$PerformanceRating <- as.factor(CaseStudy2CompSetNoAttrition$PerformanceRating)
CaseStudy2CompSetNoAttrition$RelationshipSatisfaction <- as.factor(CaseStudy2CompSetNoAttrition$RelationshipSatisfaction)
CaseStudy2CompSetNoAttrition$StockOptionLevel <- as.factor(CaseStudy2CompSetNoAttrition$StockOptionLevel)
CaseStudy2CompSetNoAttrition$WorkLifeBalance <- as.factor(CaseStudy2CompSetNoAttrition$WorkLifeBalance)
CaseStudy2CompSetNoAttrition$Education <- as.factor(CaseStudy2CompSetNoAttrition$Education)

#removing unnecessary columns
#Employee Count is all 1
CaseStudy2CompSetNoAttrition$EmployeeCount <- NULL

#Employee Number is an unnecessary ID number
CaseStudy2CompSetNoAttrition$EmployeeNumber <- NULL

#All employees are Over18
CaseStudy2CompSetNoAttrition$Over18 <- NULL

#All Employee Standard Hours are 80
CaseStudy2CompSetNoAttrition$StandardHours <-NULL

#Attritionpredict <- predict(NBmodel1, newdata = CaseStudy2CompSetNoAttrition)
#view(Attritionpredict)

```
#Correlation Plot

```{r}
numdf <- CaseStudy2[,c(2,5,7,12,18,19,20,22,26,27,29:32)]
M <- cor(numdf, use ="all.obs")
corrplot(M, method = "number", order = "alphabet")
```
#Predict Monthly Income

```{r linear regression}

model1 <- lm(MonthlyIncome ~Age+BusinessTravel+DailyRate+Department+DistanceFromHome+Education+EducationField+EnvironmentSatisfaction+Gender+HourlyRate+JobInvolvement+JobLevel+JobRole+JobSatisfaction+MaritalStatus+MonthlyRate+NumCompaniesWorked+OverTime+PercentSalaryHike+PerformanceRating+RelationshipSatisfaction+StockOptionLevel+TotalWorkingYears+TrainingTimesLastYear+WorkLifeBalance+YearsAtCompany+YearsInCurrentRole+YearsSinceLastPromotion+YearsWithCurrManager, data = CaseStudy2)

summary(model1)
anova(model1)

plot(model1$fitted.values, model1$residuals)

```
#Model 2
```{r}

model2 <- lm(MonthlyIncome~Age+BusinessTravel+Department+Education+EducationField+EnvironmentSatisfaction+Gender+HourlyRate+TotalWorkingYears, data = CaseStudy2)

summary(model2)

```
#Model 3
```{r} 

model3<- lm(MonthlyIncome ~Age+DailyRate+Department+Education+JobLevel+JobRole+NumCompaniesWorked+OverTime+PerformanceRating+TotalWorkingYears, data = CaseStudy2)

summary(model3)
confint(model3)
```
#Model 4
lm(formula = MonthlyIncome ~ Department + JobLevel + JobRole + 
    PerformanceRating + TotalWorkingYears, data = CaseStudy2)
Adjusted R-squared:  0.9521 
p-value: < 2.2e-16
```{r}
model4 <- lm(MonthlyIncome~Department+JobLevel+JobRole+PerformanceRating+TotalWorkingYears, data = CaseStudy2)
summary(model4)
confint(model4)

```
#Match NoSalary dataframe clean up to CaseStudy2
```{r}
CaseStudy2CompSetNoSalary <- read.csv("~/Desktop/CaseStudy2CompSetNoSalary.csv")
CaseStudy2CompSetNoSalary$JobSatisfaction <- as.factor(CaseStudy2CompSetNoSalary$JobSatisfaction)
CaseStudy2CompSetNoSalary$EnvironmentSatisfaction <- as.factor(CaseStudy2CompSetNoSalary$EnvironmentSatisfaction)
CaseStudy2CompSetNoSalary$JobLevel <- as.factor(CaseStudy2CompSetNoSalary$JobLevel)
CaseStudy2CompSetNoSalary$JobInvolvement <- as.factor(CaseStudy2CompSetNoSalary$JobInvolvement)
CaseStudy2CompSetNoSalary$PerformanceRating <- as.factor(CaseStudy2CompSetNoSalary$PerformanceRating)
CaseStudy2CompSetNoSalary$RelationshipSatisfaction <- as.factor(CaseStudy2CompSetNoSalary$RelationshipSatisfaction)
CaseStudy2CompSetNoSalary$StockOptionLevel <- as.factor(CaseStudy2CompSetNoSalary$StockOptionLevel)
CaseStudy2CompSetNoSalary$WorkLifeBalance <- as.factor(CaseStudy2CompSetNoSalary$WorkLifeBalance)
CaseStudy2CompSetNoSalary$Education <- as.factor(CaseStudy2CompSetNoSalary$Education)

#removing unnecessary columns
#Employee Count is all 1
CaseStudy2CompSetNoSalary$EmployeeCount <- NULL

#Employee Number is an unnecessary ID number
CaseStudy2CompSetNoSalary$EmployeeNumber <- NULL

#All employees are Over18
CaseStudy2CompSetNoSalary$Over18 <- NULL

#All Employee Standard Hours are 80
CaseStudy2CompSetNoSalary$StandardHours <-NULL
```
#Create prediction column and csv file
```{r}
MonthlyIncomepredict <- predict(model4, newdata = CaseStudy2CompSetNoSalary)


write.csv(MonthlyIncomepredict, "/Users/holliegardner/Desktop/MIpredict.csv")
```
